---
title: "Question 5 of Data Science project for R"
author: "Marcus Ting En Hao"
date: "31th March 2023"
---
Load libraries
```{r}
library(mlr3)
library(mlr3learners)
library(mlr3pipelines)
library(mlr3tuning)
```
set working directory
```{r}
setwd("C:/Users/xavie/OneDrive/Desktop/Rstudio files")
```
load data of 2007
```{r}
data7 <- read.csv("2007.csv")
```
Create new column for total delay
```{r}
data7$Totaldelay<-with(data7, paste0(DepDelay+ArrDelay+CarrierDelay+WeatherDelay+NASDelay+SecurityDelay+LateAircraftDelay))
```
Create new column for True false delay
```{r}
data7$TFSTRING[data7$Totaldelay > 0] <- 1
data7$TFSTRING[data7$Totaldelay <= 0] <- 0
```
Update data into January and February only
```{r}
data7 <- subset(data7, Month <3)
```

Update to remove rows if Diverted and Cancelled flights are True
```{r}
data7 <- subset(data7,Diverted = 1)
data7 <- subset(data7,Cancelled = 1)
```
Update to remove columns that are irrelevant to the question
```{r}
data7cut <- data7[,-c(1,5,7,10,12,14,15,16,19,20,21,23,25,26,27,28,29)]
```
Question 5
Changing important columns into factors
```{r}
data7cut$Month <- factor(data7cut$Month, order = TRUE, levels = c(1,2))
data7cut$Origin <- factor(data7cut$Origin)
data7cut$DayofMonth <- factor(data7cut$DayofMonth)
data7cut$TFSTRING <- factor(data7cut$TFSTRING)
data7cut$UniqueCarrier<- factor(data7cut$UniqueCarrier)
```
Creating the training and Testing sets
```{r}
n <- nrow(data7cut)
training_set <- sample(n, round(0.5*n))
testing_set <-setdiff(1:n, training_set)
```
Creating the task
```{r}
task <- TaskClassif$new('data7cut', backend=data7cut, target = 'TFSTRING')
task$select(c('Origin', 'DayofMonth', 'UniqueCarrier'))
measure <- msr('classif.ce')
```
Creating the conversions if data does not accept factors
```{r}
fencoder <-po("encode", method = "treatment",
               affect_columns = selector_type("factor"))
ord_to_int<- po("colapply", applicator = as.integer,
                 affect_columns = selector_type("ordered"))
```
Creating hyperparameters
```{r}
tuner <-tnr('grid_search')
terminator <-trm('evals', n_evals = 20)
```
Logistic regression
```{r}
learner_lr <- lrn("classif.log_reg")
gc_lr <- po('imputemean') %>>%
  po(learner_lr)
glrn_lr<- GraphLearner$new(gc_lr)

glrn_lr$train(task, row_ids = training_set)
glrn_lr$predict(task, row_ids = testing_set)$score() 
```


