---
title: "Question 1 of Data Science project for R"
author: "Marcus Ting En Hao"
date: "31th March 2023"
---

Load libraries
```{r}
library(DBI)
library(dplyr)
```

Set working directory

```{r}
setwd("C:/Users/xavie/OneDrive/Desktop/Rstudio files")
```

Load data of 2007 and 2008

```{r}
data7 <- read.csv("2007.csv")
data8 <- read.csv("2008.csv")
```

Create a data base. If already exist, delete it

```{r}
if (file.exists("Airdata20072008.db")) 
  file.remove("Airdata20072008.db")
```
Connect to the database
```{r}
conn <- dbConnect(RSQLite::SQLite(), "Airdata20072008.db")
```
Combine data 2007 and 2008 into 1 single dataframe
```{r}
data78 <- rbind(data7, data8)
```

Load the data into the database

```{r}
dbWriteTable(conn, "data78", data78)
```

Question 1 Best time of day to fly with minimal delay

```{r}
q1 <- dbGetQuery(conn, 
                 "SELECT deptime AS deptime, AVG(data78.DepDelay+data78.ArrDelay+data78.CarrierDelay+data78.WeatherDelay+data78.NASDelay+data78.SecurityDelay+data78.LateAircraftDelay) AS avg_delay
FROM data78
WHERE data78.Cancelled = 0 AND data78.Diverted = 0 
GROUP BY deptime
ORDER BY avg_delay")
```

Answer of Best time of day to fly with minimal delay

```{r}
print(paste(q1[1, "deptime"], "hrs is the best time of day to fly with minimal delay."))
```

Best day of the week to fly with minimal delay

```{r}
q2 <-dbGetQuery(conn,
                "SELECT dayofweek AS dayofweek, AVG(data78.DepDelay+data78.ArrDelay+data78.CarrierDelay+data78.WeatherDelay+data78.NASDelay+data78.SecurityDelay+data78.LateAircraftDelay) AS avg_delay
FROM data78
 WHERE data78.Cancelled = 0 AND data78.Diverted = 0 
GROUP BY dayofweek
ORDER BY avg_delay")
```

Answer of Best day of the week to fly with minimal delay

```{r}
print(paste(q2[1, "dayofweek"], "is the best day of the week to fly with minimal delay."))
```

Best year to fly with minimal delay

```{r}
q3 <-dbGetQuery(conn,
                "SELECT year AS year, AVG(data78.DepDelay+data78.ArrDelay+data78.CarrierDelay+data78.WeatherDelay+data78.NASDelay+data78.SecurityDelay+data78.LateAircraftDelay) AS avg_delay
FROM data78
 WHERE data78.Cancelled = 0 AND data78.Diverted = 0 
GROUP BY year
ORDER BY avg_delay")
```

Answer of Best year to fly with minimal delay

```{r}
print(paste(q3[1, "year"], "is the best year to fly with minimal delay."))

```



