---
title: "Question 2 of Data Science project for R"
author: "Marcus Ting En Hao"
date: "31th March 2023"
---
Load libraries
```{r}
library(DBI)
library(dplyr)
```
Set working directory
```{r}
setwd("C:/Users/xavie/OneDrive/Desktop/Rstudio files")
```
Load data of 2007, 2008 and planes
```{r}
planes <- read.csv("plane-data.csv", header = TRUE)
data7 <- read.csv("2007.csv")
data8 <- read.csv("2008.csv")
```
Combine data 2007 and 2008 into 1 single dataframe
```{r}
data78 <- rbind(data7, data8)
```
Create a data base. If already exist, delete it
```{r}
if (file.exists("Airdata20072008.db")) 
  file.remove("Airdata20072008.db")
```
Connect to database
```{r}
conn <- dbConnect(RSQLite::SQLite(), "Airdata20072008.db")
```
Load data into database
```{r}
dbWriteTable(conn, "planedata", planes)
dbWriteTable(conn, "data78", data78)
```
Getting the average delay of oldest model
```{r}
q4 <-dbGetQuery(conn,
                "SELECT model AS model, AVG(data78.DepDelay+data78.ArrDelay+data78.CarrierDelay+data78.WeatherDelay+data78.NASDelay+data78.SecurityDelay+data78.LateAircraftDelay) AS avg_delay, planedata.year AS year
FROM planedata JOIN data78 USING(tailnum)
WHERE data78.Cancelled = 0 AND data78.Diverted = 0 AND planedata.year > 0 
GROUP BY model
ORDER BY year")           
```

Getting the average delay of newest model

```{r}
q5 <-dbGetQuery(conn,
                "SELECT model AS model, AVG(data78.DepDelay+data78.ArrDelay+data78.CarrierDelay+data78.WeatherDelay+data78.NASDelay+data78.SecurityDelay+data78.LateAircraftDelay) AS avg_delay, planedata.year AS year
FROM planedata JOIN data78 USING(tailnum)
WHERE data78.Cancelled = 0 AND data78.Diverted = 0 AND planedata.year > 0 AND planedata.year != 'None'
GROUP BY model
ORDER BY year DESC") 
```
Put new Queries into buckets
```{r}
oldmodel=paste(q4[1, "model"])
newmodel=paste(q5[1, "model"])
```
Changing Queries into str
```{r}
oldavgdelaystring=paste(q4[1,"avg_delay"])
newavgdelaystring=paste(q5[1,"avg_delay"])
```
Converting avgdelays into numeric for more than/less than
```{r}
oldavgdelay=as.numeric(oldavgdelaystring)
newavgdelay=as.numeric(newavgdelaystring)

```
Setting the conditional
```{r}
if(oldavgdelay>newavgdelay){
  answerq4q5 = TRUE
}else {answerq4q5 = FALSE
}
```
Answer for question 2
```{r}
message("The oldest plane model, which is the " ,oldmodel, ", has an average delay of ", oldavgdelay, 
        ", while the newest plane model, which is the ", newmodel, ", has an average delay of ", newavgdelay, 
        ". Therefore we can conclude that with the given data, the statement of 'older planes suffer more delays' to be ", answerq4q5)
```




